Global patterns of forest autotrophic carbon fluxes

### 2020-01-17 manuscript/manuscript draft.Rmd
cropped Fig. 1 map
cropped manually.

```{r echo=FALSE, out.width='100%', fig.cap = "Map showing all data used in the analysis, coded by variable", fig.pos='H'}
  knitr::include_graphics("distribution_all_variables.png")
```
*Data selection.* Over 50 variables of forest carbon stocks and annual fluxes are represented in the ForC database; this analysis focussed on measures of primary productivity. Table 1 contains details of the variables selected for analysis.

>>>>

```{r echo=FALSE, out.width='100%', fig.cap = "Map showing all data used in the analysis, coded by variable. Variables are plotted individually in Fig. S1. ", fig.pos='H'}
  knitr::include_graphics("distribution_all_variables_cropped.png")
```
*Data selection.* Over 50 variables of forest carbon stocks and annual fluxes are represented in the ForC database; this analysis focussed on measures of primary productivity. Table 1 contains details of the variables selected for analysis.
